\begin{thebibliography}{00}
    \bibitem{b1} S. Pollard, M. Pilu, S. Hayes, and A. Lorusso, “View synthesis by
    trinocular edge matching and transfer,” Image Vis. Comput., vol. 18,
    pp. 749–757, 2000.
    \bibitem{b2} H. Saito, S. Baba, and T. Kanade, “Appearance-based virtual view
    generation from multicamera videos captured in the 3-D room,” IEEE
    Trans. Multimedia, vol. 5, no. 3, pp. 303–316, Sep. 2003.
    \bibitem{b3} S. M. Seitz and C. R. Dyer, “Photorealistic scene reconstruction by
    voxel coloring,” in Proc. Computer Vision and Pattern Recognition
    (CVPR1997), 1997, pp. 1067–1073.
    
    \bibitem{b4} Takeo Kanade, Peter Rander, and PJ Narayanan, “Virtualized reality:
    Constructing virtual worlds from real scenes,” IEEE multimedia, vol.
    4, no. 1, pp. 34–47, 1997.
    \bibitem{b5} Takashi Matsuyama and Takeshi Takai, “Generation, visualization,
    and editing of 3d video,” in null. IEEE, 2002, p. 234.
    \bibitem{b6} Jean-Yves Guillemaut and Adrian Hilton, “Joint multi-layer segmentation 
    and reconstruction for free-viewpoint video applications,”
    International journal of computer vision, vol. 93, no. 1, pp. 73–100,
    2011.
    \bibitem{b7} Marcel Germann, Tiberiu Popa, Richard Keiser, Remo Ziegler, and
    Markus Gross, “Novel-view synthesis of outdoor sport events using
    an adaptive view-dependent geometry,” in Computer Graphics Forum.
    Wiley Online Library, 2012, vol. 31, pp. 325–333.
    \bibitem{b8} Keisuke Nonaka, Ryosuke Watanabe, Jun Chen, Houari Sabirin, and
    Sei Naito, “Fast plane-based free-viewpoint synthesis for real-time
    live streaming,” in IEEE International Conference on Visual Communications 
    and Image Processing. IEEE, 2018.


    % read paper
    \bibitem{iview2.1} Grau, Oliver and Thomas, Graham and Hilton, Adrian and Kilner, J. and Starck, Jonathan. (2007). 
    A Robust Free-Viewpoint Video System for Sport Scenes. 1 - 4. 10.1109/3DTV.2007.4379384.
\end{thebibliography}

% @inproceedings{inproceedings,
% author = {Grau, Oliver and Thomas, Graham and Hilton, Adrian and Kilner, J. and Starck, Jonathan},
% year = {2007},
% month = {06},
% pages = {1 - 4},
% title = {A Robust Free-Viewpoint Video System for Sport Scenes},
% isbn = {978-1-4244-0721-7},
% doi = {10.1109/3DTV.2007.4379384}
% }